---
title: "_**SNR Prediction on the CMTS Data**_"
author: "_By Cypriyan_"
date: "December 13, 2019"
output: html_document
---
\
\
\
_**Linear Modelling Algorithm Step by Step**_  
\
\
__Import The Raw Input Data into the Environment__
```{r}
cmts <- read.csv("C:/Users/HOME/Downloads/boo.csv", stringsAsFactors=TRUE)
```
\
__Structure of the Input Data__
```{r}
str(cmts)

```
\
__Checking Correlation on Categorical Variables__
```{r, warning= FALSE}
library(GoodmanKruskal)
cmts1 <- subset(cmts, select = c(hub, cmts_name))
gk_matrix <- GKtauDataframe(cmts1)
plot(gk_matrix, corrColors = "blue")

```
\
\
\
__Deleting Uni_Dimensional, Multi-Dimensional & Correlated Categorical variables__
```{r}
cmts$as_of_dt <- NULL
cmts$hr <- NULL
cmts$Market <- NULL
cmts$hub <- NULL
cmts$mac_addr <- NULL
cmts$crte_dtm <- NULL
cmts$data_acq_id <- NULL
cmts$dt <- NULL
cmts$hour <- NULL

```

```{r,echo=FALSE}
cmts <- read.csv("C:/Users/HOME/Downloads/boo.csv", stringsAsFactors=FALSE)
cmts$as_of_dt <- NULL
cmts$hr <- NULL
cmts$Market <- NULL
cmts$hub <- NULL
cmts$mac_addr <- NULL
cmts$crte_dtm <- NULL
cmts$data_acq_id <- NULL
cmts$dt <- NULL
cmts$hour <- NULL
```
\
__Scatter Plot of Independents with the Dependent Varaiable (Signal with all the Independents)__         
__Linear line can be either Upward or Downward__
```{r}
plot(cmts$cer_up, cmts$snr_up, main = "Scatter Plot of Cer_up & SNR", xlab = "CER_UP", ylab = "SNR") # Negative
abline(lm(snr_up ~ cer_up, data = cmts), col = "red")
plot(cmts$ccer_up, cmts$snr_up, main = "Scatter Plot of CCer_up & SNR", xlab = "CCER_UP", ylab = "SNR")# Negative
abline(lm(snr_up ~ ccer_up, data = cmts), col = "red")

```

```{r}
plot(cmts$rxpower_up, cmts$snr_up,  main = "Scatter Plot of Receiver Power & SNR", xlab = "RxPwr", ylab ="SNR")# Positive
abline(lm(snr_up ~ rxpower_up, data = cmts), col = "red")
plot(cmts$tspower_up, cmts$snr_up, main = "Scatter Plot of Tranmission Power & SNR",xlab = "TxPwr", ylab ="SNR")# Positive
abline(lm(snr_up ~ tspower_up, data = cmts), col = "red")
```
\
__Outlier Treatment - Capping it to (Mean + 3*Std Deviation as Maximum) & (Mean - 3*Std Deviation as Minimun)__      
__For Variables such as Cer_up, Ccer_up, TsPower_up, RxPower_up & Path_loss_up__
```{r, warning=FALSE, results= "hide"}
library(psych)

describeBy(cmts$cer_up)
0.09 + 3*1.58 # 4.83
0.09 - 3*1.58 # -4.65
cmts$new_cer <- ifelse(cmts$cer_up >= 5, 5, cmts$cer_up)



describeBy(cmts$ccer_up)
1.21 + 3* 5.96 # 19.09
1.21 - 3* 5.96 # -16.67
cmts$new_ccer <- ifelse(cmts$ccer_up >= 20, 20, cmts$ccer_up)



describeBy(cmts$tspower_up)
45.83 + 3 * 8.58 # 71.57
45.83 - 3 * 8.58 # 20.09
cmts$new_tspower <- ifelse(cmts$tspower_up <= 20, 20, cmts$tspower_up)




describeBy(cmts$rxpower_up)
-0.1 + 3 * 1.03 # 2.99
-0.1 - 3 * 1.03 # -3.19
cmts$new_rxpower <- ifelse(cmts$rxpower_up >= 3.5, 3.5,
                    ifelse(cmts$rxpower_up < -3.75, -3.75, cmts$rxpower_up))




describeBy(cmts$path_loss_up)
45.92 + 3 * 8.8 # 72.32
45.92 - 3 * 8.8 # 19.52
cmts$new_pathlossup <- ifelse(cmts$path_loss_up <= 19, 19, cmts$path_loss_up)




cmts$cer_up <- NULL
cmts$ccer_up <- NULL
cmts$tspower_up <- NULL
cmts$rxpower_up <- NULL
cmts$path_loss_up <- NULL

```
\
__Subset the dataset into only Numericals to check the Correlation aspect between them__
```{r, warning= FALSE, }
cmts_cor <- subset(cmts, select = c(new_cer, new_ccer, new_rxpower, new_tspower, 
                                    new_pathlossup))
library(sp)
library(raster)
library(usdm)


vif_cmts <- vifstep(cmts_cor, th = 10)
vif_cmts

vif(cmts_cor)

cmts$new_pathlossup <- NULL

```
\
__SubString the Variable Upstream_Name & Deleting the rows which are having 0 as Signal values from the SNR__
```{r}
cmts$cableID <- substr(cmts$upstream_name, 33, 52)
cmts$cmts_port <- substr(cmts$upstream_name, 20, 31)

cmts$cableID1 <- as.factor(cmts$cableID)
cmts$cmts_port1 <- as.factor(cmts$cmts_port)

cmts$cmts_port <- NULL
#cmts$cmts_port1 <- NULL
cmts$cableID <- NULL
cmts$upstream_name <- NULL

cmts <- cmts[!cmts$snr_up == 0 , ]

```
\
__Dividing the CMTS dataset into Train & Test datasets at 70 & 30 percent respectively__
```{r,warning= FALSE}
library(caTools)

samp_size <- floor(0.7 * nrow(cmts))
set.seed(123)

train_cmts <- sample(seq_len(nrow(cmts)), size = samp_size)
train_cmts1 <- cmts[train_cmts,]
test_cmts <- cmts[-train_cmts,]


```
\
__Running the Linear Model Algorithm on the Train dataset__
```{r, echo = FALSE}
mod <- lm(snr_up ~ . , data = train_cmts1)
summary(mod)

```
\
__Model Validation on the Test Dataset showing the Predicted Signal Values from the model as against its Actual Values__
```{r, warning= FALSE}
library(lattice)
library(grid)
library(DMwR)

distpre <- as.data.frame(predict(mod, test_cmts))
head(distpre)

actuals_preds <- data.frame(cbind(Snr_up_actuals = test_cmts$snr_up, 
                            Snr_up_predicteds = distpre$`predict(mod, test_cmts)`))
head(actuals_preds)
correlationaccuracy <- cor(actuals_preds)
correlationaccuracy 

```

__Model Validation with scores such as MAPE & RMSE (MAPE - Mean Absolute Percentage Error) & (RMSE -Root Mean square error)__

```{r}
DMwR::regr.eval(actuals_preds$Snr_up_actuals, actuals_preds$Snr_up_predicteds)


```


# The End. 
